### 2019-11-13 cvpr_submission/introduction.tex
Update introduction.tex

\section{Introduction}
In recent years, neural networks, at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became dominating solutions across many domains, from  Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural} among others.
At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}); i.e. sampled from a common input space under similar data distribution characteristics.
However, in many real-world scenarios, this assumption does not hold. Moreover, as modern neural models often have  millions of trainable parameters, training them requires vast amount of data, which for some domains (notably medical) can be very expensive and/or extremely difficult to collect.
One of the widely accepted solutions for the problems mentioned above is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enables model - and thus performance - improvements by transferring \emph{information} from one domain to another.

@@

In computer vision, it is now standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
That such transfer improves performance is appealing, knowing that both the domain (e.g. realistic images vs. medical ones or images with cars) and the task (e.g. image classification vs. VQA or image segmentation) can change significantly. This type of transfer learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.

A similar development can be noted in the Natural Language Processing (NLP) community.
Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses coming from e.g.\ Wikipedia or Twitter, became a standard procedure when working with different NLP domains and tasks, some where labeled data is less accessible.
Recently, we can denote an accelerated development of deep contextualized word representations such as ELMo (based on bidirectional LSTMs)~\cite{peters2018deep} or BERT (based on the Transformer~\cite{vaswani2017attention} architecture)~\cite{devlin2018bert}, which pretrain an entire network (and not just the input layer) on very large amount of data.
Analogically to the pretrained image encoders, the community is facilitating access to such pretrained models through repositories, some with dozens of pretrained BERT variations. HuggingFace~\cite{wolf2019transformers} is one of the most notable examples.

The success of transfer learning raises several questions, such as which characteristics make a dataset favorable for use in pretraining (notably ImageNet~\cite{huh2016makes}), or what explains the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
One of the most systematic work studying the impact of transfer learning in computer vision is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, aiming at discovering the dependencies across a dictionary of twenty-six 2D, 2.5D, 3D, and semantic tasks.

The impact of transfer learning is even more central in the case of multi-modal tasks~\cite{mogadala2019trends}, combining both of the modalities mentioned above (i.e. vision and language).
One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer natural language questions by taking into account the content of a single image (Image Question Answering) or several frames (Video Question Answering).
In a typical VQA model, setting aside whether it is performing an early fusion of embeddings of those two modalities~\cite{malinowski2018visual} or multi-step reasoning~\cite{hudson2018compositional}, using pretrained image encoders and word embeddings is de facto standard, having empirically proven its dominance over the models trained from the ground up.

In this work, we are focusing on a parallel aspect of transfer learning. As both Image and Video QA can be seen as meta-problems, where the model has to develop a different reasoning process depending on the type/family of question (task, e.g. counting objects or finding the value of a specific object's attribute), we asked ourselves whether mastering one task type/family can help with mastering others. This work is thus also deeply related to multi-task learning~\cite{caruana1997multitask}.

>>>>

\section{Introduction}
In recent years, neural networks, being at the epicenter of the Deep Learning~\cite{lecun2015deep} revolution, became the dominant solutions across many domains, from  Speech Recognition~\cite{graves2013speech}, Image Classification~\cite{krizhevsky2012imagenet}, Object Detection~\cite{redmon2016you}, to Question Answering~\cite{weston2014memory} and Machine Translation~\cite{bahdanau2014neural} among others.
At their core, being statistical models~\cite{ripley1993statistical,warner1996understanding}, neural networks rely on the assumption that training and testing samples are independent and identically distributed (\textit{iid}); i.e. sampled from a common input space under similar data distribution characteristics.
However, in many real-world scenarios, this assumption does not hold. Moreover, as modern neural models often have  millions of trainable parameters, training them requires vast amounts of data, which for some domains (e.g., medical) can be very expensive and/or extremely difficult to collect.
One of the widely used solutions for the above mentioned problems is Transfer Learning~\cite{pan2009survey,weiss2016survey}, a technique which enhances the  model performance by transferring \emph{information} from one domain to another.

@@

In computer vision, it is now a standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
Such performance improvements are appealing, especially for cases that both the domain (e.g. realistic images vs. medical ones or images with cars) and the task (e.g. image classification vs. VQA or image segmentation) can change significantly. This type of transfer learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.

A similar development has emerged in the Natural Language Processing (NLP) community.
Using shallow word embeddings, such as word2vec~\cite{mikolov2013distributed} or GloVe~\cite{pennington2014glove}, pretrained on large corpuses coming from e.g.\ Wikipedia or Twitter, became a standard procedure when working with different NLP domains and tasks, especially when labeled data is less accessible.
Recently, we observe a growing utilization of deep contextualized word representations such as ELMo (based on bidirectional LSTMs)~\cite{peters2018deep} or BERT (based on the Transformer~\cite{vaswani2017attention} architecture)~\cite{devlin2018bert}, which pretrain an entire network (and not just the input layer) on very large amounts of data.
In analogy to the pretrained image encoders, the community is facilitating access to such pretrained models through repositories, some with dozens of pretrained BERT variations. HuggingFace~\cite{wolf2019transformers} is one of the most notable examples.

The success of transfer learning raises several questions for research, such as the characteristics which make a dataset more favorable to use in pretraining (notably ImageNet~\cite{huh2016makes}), or regarding the observed performance correlation of models with different architectures between the source and target domains~\cite{kornblith2019better}.
One of the most systematic in this area is the computational taxonomic map for task transfer learning~\cite{zamir2018taskonomy}, which aim to discover the dependencies across a dictionary of twenty-six 2D, 2.5D, 3D, and semantic tasks.

The impact of transfer learning is even more essential in the case of multi-modal tasks, \cite{mogadala2019trends}, which combine both modalities mentioned above (i.e. vision and language).
%One of the most popular problem domain is Visual Question Answering (VQA)~\cite{malinowski2014multi,antol2015vqa}, where the system is expected to answer natural language questions by taking into account the content of a single image (Image Question Answering) or several frames (Video Question Answering).
%In a typical VQA model, setting aside whether it is performing an early fusion of embeddings of those two modalities~\cite{malinowski2018visual} or multi-step reasoning~\cite{hudson2018compositional}, using pretrained image encoders and word embeddings is de facto standard, having empirically proven its dominance over the models trained from the ground up.
In this work, we focus on a parallel aspect of transfer learning. As both Image and Video QA can be seen as meta-problems, where the model has to develop a different reasoning process depending on the type/family of question (task, e.g. counting objects or finding the value of a specific object's attribute), we investigated  whether mastering one task type/family can help to master others.  Thus, this work is also deeply related to multi-task learning~\cite{caruana1997multitask}.
